Probabilistic Passphrase Cracking

### 2018-02-07 paper/paper.tex
Paper: spell-checked (committing binary pdf and tex), resolved a todo

In this work, we attempted to find and implement the most effective method. We
compared Markov chains, n-grams and a hybrid dictionary attack. The latter was
found to be most effective, both in terms of efficiency and the number of
results. Excluding the time required to build the dictionary from English
Wikipedia and Wikiquote articles, it took only 10 minutes to crack over 2.3
million unique passphrases by using a hybrid dictionary attack with hashcat.
Future users could download such a dictionary without having to compile it
manually from various sources.

@@

We classify this attack as a hybrid dictionary attack, because of the
similarity to traditional hybrid dictionary attacks on passwords. In suchs
attacks, a large list of words is used together with mangling rules to generate
possible permutations. In Labrande's variant, phrases are used instead of
words, using a smart method of selecting likely phrases.

@@

% TODO: word choice (global): entries or records? Or something else?

@@

The n-gram phrase generator first loads the data, which takes a few minutes and
scales linearly with the n-gram file size. While running, it generates two to
four million phrases per second on a single CPU core (the median is 3.3 million
phrases per second). This saturated Hashcat's ability to process input: hashcat
processes around ten million SHA-1 hashes per second, but applies a few rules.
Since rules easily generate many more than three variants per phrase, the speed
of our program is sufficient despite running on only a single core and being
written in Python, an interpreted language.

>>>>

In this work, we attempted to find and implement the most effective method. We
compared Markov chains, n-grams and a hybrid dictionary attack. The latter was
found to be most effective, both in terms of efficiency and the number of
results. Excluding the time required to build the dictionary from English
Wikipedia and Wikiquote articles, it took only 10 minutes to crack over 2.3
million unique passphrases by using a hybrid dictionary attack with Hashcat.
Future users could download such a dictionary without having to compile it
manually from various sources.

@@

We classify this attack as a hybrid dictionary attack, because of the
similarity to traditional hybrid dictionary attacks on passwords. In such
attacks, a large list of words is used together with mangling rules to generate
possible permutations. In Labrande's variant, phrases are used instead of
words, using a smart method of selecting likely phrases.

@@

@@

The n-gram phrase generator first loads the data, which takes a few minutes and
scales linearly with the n-gram file size. While running, it generates two to
four million phrases per second on a single CPU core (the median is 3.3 million
phrases per second). This saturated Hashcat's ability to process input: Hashcat
processes around ten million SHA-1 hashes per second, but applies a few rules.
Since rules easily generate many more than three variants per phrase, the speed
of our program is sufficient despite running on only a single core and being
written in Python, an interpreted language.
